---
title: "Basic PaAnalysis of Enron Emails"
output:
  html_document:
    df_print: paged
---

Begin by parsing the data to extract headers from all emails.  Write headers to a CSV file.  I found a few emails with characters that could not be encoding, which I fixed by hand.  Interestingly, these emails were from Enron Japan, expressing concerns to management.

```{r}
source('../src/parse_input.R')
con <- file('headers.csv',open="w")
header <- create_csv_columns()
writeLines(header, con, sep="\n")
process_all_headers('../data/maildir', con)
close(con)
```

Get some basic counts from the headers, including number of senders, number of recipents, number of messages and number of people.

```{r}
source('../src/format_utils.R')
headers <- load_headers('headers.csv')
nrow(headers)
```

See the number of emails by sender

```{r}
headers %>%
  group_by(From) %>%
  summarise(Count=n()) %>%
  arrange(desc(Count))
```

See the number of emails by receiver

```{r}
recipients <- collect_recipients(headers)
recipients %>%
  group_by(recipient) %>%
  summarise(Count=n()) %>%
  arrange(desc(Count))
```

Let's find the date range of emails.  There are some outliners and really bad dates.  (TODO: investigate later if there is time about 1490 rows probably using a different date format.)  These may just have the wrong date.  Bins of roughly a month

```{r}
headers %>% 
  ggplot(aes(Date)) + 
  geom_freqpoly(binwidth = 86400*7*4)
headers %>%
  filter(year(Date)< 1999 | year(Date) > 2003) %>%
  arrange(Date)
```

Adjusting for the outlines, we see emails by week

```{r}
headers %>% 
  filter(year(Date) > 1999 & year(Date) < 2003) %>%
  ggplot(aes(Date)) + 
  geom_freqpoly(binwidth = 86400*7)
```
