---
title: "User Topic Analysis"
output:
  html_document:
    df_print: paged
---

Create a topic model on three different users.  See if we can then match emails to users.  A lot of this content was inspired by (https://www.tidytextmining.com/topicmodeling.html)[Topic Mining].

```{r}
source('../src/format_utils.R')
headers <- load_headers('headers.csv')
steven <- "steven.kean@enron.com" # 6759 emails - Vice President and Chief of Staff
phillip <- "phillip.allen@enron.com" # 2195 emails
mike <- "mike.carson@enron.com" # 721 emails
```

Create a data frame with all the emails from the three different authors

```{r}
source('../src/lda.R')
authors <- data_frame(author=c(steven, phillip, mike))
email_df <- get_tidy_email_from_authors(headers, authors)
email_dtm <- get_dtm_from_authors(email_df)
email_df
```

Use the LDA algorithm to do a topic analysis, in which each author corresponds to a topic (ideally).  The Beta matrix is the probability that a term was generated from a topic.  LDA is a generative probabilistic model, that assumes a Dirichlet prior over the latent topics.

```{r}
require(topicmodels)
email_dla <- LDA(email_dtm, k = 3, control = list(seed = 1719))
email_topics <- tidy(email_dla, matrix = "beta")
``` 

Visualize the top terms in each of the three categories

```{r}
require(ggplot2)
top_terms <- email_topics %>%
  group_by(topic) %>%
  top_n(5, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)
top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

See how well emails align with topic.  Use the gamma matrix, which is a per-document-per-topicp probability.  We'll also

```{r}
email_gamma <- tidy(email_dla, matrix = "gamma") %>%
   separate(document, c("author", "email"), sep = "_", convert = TRUE)
email_gamma
```

View the probability of each email against each each topic.  This shows that the classification isn't very clean.  Phillip corresponds mostly to category one; Steven corresponds to category two; and Mike corresponds to category 3.

```{r}
email_gamma %>%
  mutate(title = reorder(author, gamma * topic)) %>%
  ggplot(aes(factor(topic), gamma)) +
  geom_boxplot() +
  facet_wrap(~ title)
```

Use the topics to classify each email.

```{r}
email_classifications <- email_gamma %>%
  group_by(author, email) %>%
  top_n(1, gamma) %>%
  ungroup()
email_topics <- email_classifications %>%
  count(author, topic) %>%
  group_by(author) %>%
  top_n(1, n) %>%
  ungroup() %>%
  transmute(consensus = author, topic)
email_classifications
email_topics
```

Create a visual display of a confusion matrix.  Mike's emails are attributed mostly to him.  However, there is a lot of confusion between Phillip and Steven, suggesting that they author emails on similar topics.

```{r}
require(scales)
augment(email_dla, data = email_dtm) %>%
  separate(document, c("author", "email"), sep = "_", convert = TRUE) %>%
  inner_join(email_topics, by = c(".topic" = "topic")) %>%
  count(author, consensus, wt = count) %>%
  group_by(author) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(consensus, author, fill = percent)) +
  geom_tile() +
  scale_fill_gradient2(high = "red", label = percent_format()) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        panel.grid = element_blank()) +
  labs(x = "Authors were assigned to",
       y = "Author words came from",
       fill = "% of assignments")

```

